Applying LIME to Bullet Data Research Journal

### 2019-01-30 journal/applying LIME to bullet data journal.Rmd
finished updating code with rfscore based bins (finally!)

I computed kappa for each bin situation separately for the top three features chosen. These values are plotted below for each set. For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the nubmer of bins followed by the tree based bins. The values of kappa for the quantile bins are slight to fair agreement. For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.

@@

```{r eval = FALSE}
hamby224_sensitivity <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))

# Code for organizing the sensitivity analysis results
hamby224_sensitivity_results <- hamby224_sensitivity %>%
  group_by(set, rep, situation, bin_situation, nbins) %>%
  summarise(mse = sum((diff)^2) / length(diff),
            ave_r2 = mean(model_r2))
```

The plot below shows boxplots of the 10 mean squared errors computed for each of the input situations for each set. There does not appear to be much variation for most of the cases. The largest amount of variation occurs with 4 and 5 equally spaced bins. There is moderate variability for 3 equally spaced bins, but all of the 10 runs resulted in much lower mses than any of the other situations. This still seems to support the choice of using 3 equally spaced quantile bins for both sets.

```{r eval = FALSE}
# Plots the MSEs from the sensativity analysis
hamby224_sensitivity_results %>%
  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
  ggplot(aes(x = situation, y = mse)) + 
  geom_boxplot(aes(color = bin_situation)) +
  facet_grid(set ~ bins, scales = "free_x") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
  labs(x = "Situation", y = "MSE", color = "") + 
  scale_color_brewer(palette = "RdYlBu")
```

```{r eval = FALSE}
# Plots the average R^2 value from the sensativity analysis 
hamby224_sensitivity_mses %>%
  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
  ggplot(aes(x = situation, y = ave_r2)) + 
  geom_boxplot(aes(color = bin_situation)) +
  facet_grid(set ~ bins, scales = "free_x") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
  labs(x = "Situation", y = "MSE", color = "") + 
  scale_color_brewer(palette = "RdYlBu")
```

```{r eval = FALSE}
hamby224_consistency <- hamby224_sensitivity_results %>%
  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, nbins, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(set, situation, bin_situation, nbins, case) %>%
  summarise(nlevels = length(levels(factor(feature))),
            count = n()) %>%
  ungroup() %>%
  group_by(set, situation, bin_situation, nbins) %>%
  summarise(mean_nlevels = mean(nlevels),
            sd_nlevels = sd(nlevels),
            upper = mean(nlevels) + sd(nlevels),
            lower = mean(nlevels) - sd(nlevels),
            max = max(nlevels),
            min = min(nlevels))
```

@@

```{r eval = FALSE}
hamby224_consistency %>%
  mutate(bins = ifelse(nbins == 4 & bin_situation == "other", "other", as.character(nbins))) %>%
  ggplot(aes(x = situation, y = mean_nlevels)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
  geom_point(aes(color = bin_situation)) + 
  facet_grid(set ~ bins, scales = "free_x") + 
  labs(x = "Situation", y = "Mean Number of Features", color = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
  scale_color_brewer(palette = "RdYlBu")
```

The bar chart below shows the proportion of different number of top features chosen across all test cases within a set for each input situation. This shows that the most different features chosen was four. However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.

```{r eval = FALSE}
hamby224_sensitivity_results %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(set, situation, case) %>%
  summarise(nlevels = length(levels(factor(feature)))) %>%
  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
  ggplot(aes(x = situation, fill = nlevels)) + 
  geom_bar(position = "stack") +
  facet_grid( ~ set) + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(x = "Situation", y = "Count", fill = "Number of Features")

hamby224_sensitivity_results %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, case, rep) %>%
  slice(2) %>%
  ungroup() %>%
  group_by(set, situation, case) %>%
  summarise(nlevels = length(levels(factor(feature)))) %>%
  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
  ggplot(aes(x = situation, fill = nlevels)) + 
  geom_bar(position = "stack") +
  facet_grid( ~ set) + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(x = "Situation", y = "Count", fill = "Number of Features")

hamby224_sensitivity_results %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, case, rep) %>%
  slice(3) %>%
  ungroup() %>%
  group_by(set, situation, case) %>%
  summarise(nlevels = length(levels(factor(feature)))) %>%
  mutate(nlevels = factor(nlevels, levels = c(1:5))) %>%
  ggplot(aes(x = situation, fill = nlevels)) + 
  geom_bar(position = "stack") +
  facet_grid( ~ set) + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(x = "Situation", y = "Count", fill = "Number of Features")
```

The plot below needs some work, but it does contain some interesting information. Right now, I am only concentrating on set 1. We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case. We can also see that different variables are selected as important depending on the number of bins. It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases. On the other hand, the quantile bins choose different first variables for the cases.

@@

```{r fig.height = 8, fig.width = 10, eval = FALSE}
hamby224_sensitivity_results %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_brewer(palette = "Spectral") + 
  labs(x = "cases")

hamby224_sensitivity_results %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(2) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_brewer(palette = "Spectral") + 
  labs(x = "cases")

hamby224_sensitivity_results %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(3) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 17)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_brewer(palette = "Spectral") + 
  labs(x = "cases")
```

@@

```{r eval = FALSE}
hamby224_test %>% 
  select(rf_features, rfscore, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, rfscore, samesource) %>%
  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
  geom_point() + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
       title = "Hamby 224 Testing Data") +
  theme_bw() +
  theme(legend.position = "bottom")

```

@@

```{r eval = FALSE}
joined_results <- hamby224_lime_results %>%
  select(set, situation, mse, ave_r2) %>%
  full_join(hamby224_sensitivity_mses %>%
              group_by(set, situation) %>%
              summarise(mean_sensitivity_mse = mean(mse), 
                        sd_sensitivity_mse = sd(mse)),
            by = c("set", "situation")) %>%
  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
            by = c("set", "situation")) %>%
  group_by(set) %>%
  mutate(mse_order = dense_rank(mse),
         ave_r2_order = dense_rank(desc(ave_r2)),
         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
         mean_nlevels_order = dense_rank(mean_nlevels))
```

```{r eval = FALSE}
joined_results %>%
  ungroup() %>%
  filter(set == "Set 1") %>%
  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
                rownames = FALSE,
                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
                             "Mean R2"),
                caption = "Results from Set 1")

@@

# Future Ideas to Implement

* Include a penalty for the number of parameters when choosing bins
* Look at the AUC after binning
* Compare the simple models based on different number of bins using an F-test
* Determine the best number of bins to use for each variable

>>>>

I computed kappa for each bin situation separately for the top three features chosen. These values are plotted below for each set. For both the first and second features chosen by lime, the values of kappa suggest that quantile bins are the most consistent across all the number of bins followed by the tree based bins. The values of kappa for the quantile bins are slight to fair agreement. For the third chosen variable, the tree based bins have the highest value of kappa, but all the kappa values for the third chosen feature are low.

@@

```{r}
# Join the sensativity outputs with the test data
hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, 
           set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))
```

```{r}
# Code for organizing the sensitivity analysis results
hamby224_sensitivity_results <- hamby224_sensitivity_joined %>%
  group_by(set, rep, situation, bin_situation, nbins) %>%
  summarise(mse = sum((diff)^2) / length(diff),
            ave_r2 = mean(model_r2))
```

The plot below shows boxplots of the mean squared errors computed for each of the input situations for each set. There does not appear to be much variation for most of the cases. The largest amount of variation occurs with 4 and 5 equally spaced bins. There is moderate variability for 3 equally spaced bins. The lowest MSEs occur for the samesource tree based bins followed by the rfscore tree based bins for most cases.

```{r}
# Plots the MSEs from the sensativity analysis
hamby224_sensitivity_results %>%
  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
                       "other", as.character(nbins))) %>%
  ggplot(aes(x = bin_situation, y = mse)) + 
  geom_boxplot(aes(color = bin_situation)) +
  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
  labs(x = "Bin Type", y = "MSE", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

The plot blow shows boxplots of the average $R^2$ values from the 10 models for all input options and for each set. There is minimal variability in the average $R^2$ value for all cases, and the relationships between $R^2$ values and input cases agree with the single implementation seen below.

```{r}
# Plots the average R^2 value from the sensativity analysis 
hamby224_sensitivity_results %>%
  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"),
                       "other", as.character(nbins))) %>%
  ggplot(aes(x = bin_situation, y = ave_r2)) + 
  geom_boxplot(aes(color = bin_situation)) +
  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") +
  labs(x = "Bin Type", y = "MSE", color = "") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

@@

```{r}
# Determine and plot the average and variability of the number levels for each case 
# and input option
hamby224_consistency <- hamby224_sensitivity_joined %>%
  select(set, situation, bin_situation, nbins, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(set, situation, nbins, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(set, situation, bin_situation, nbins, case) %>%
  summarise(nlevels = length(levels(factor(feature))),
            count = n()) %>%
  ungroup() %>%
  group_by(set, situation, bin_situation, nbins) %>%
  summarise(mean_nlevels = mean(nlevels),
            sd_nlevels = sd(nlevels),
            upper = mean(nlevels) + sd(nlevels),
            lower = mean(nlevels) - sd(nlevels),
            max = max(nlevels),
            min = min(nlevels)) %>%
  mutate(bins = ifelse(bin_situation %in% c("kernel density", "normal approximation"), 
                       "other", as.character(nbins)))

hamby224_consistency %>%
  ggplot(aes(x = situation, y = mean_nlevels)) + 
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "grey80") +
  geom_point(aes(color = bin_situation)) + 
  facet_grid(set ~ bins, scales = "free_x", space = "free_x") + 
  labs(x = "Bin Type", y = "Mean Number of Features", color = "") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
  scale_color_gretchenalbrecht(palette = "winged_spill", discrete = TRUE)
```

The bar chart below shows the proportion of different number of first, second, and third features chosen across all test cases within a set for each input situation. This shows that the most different features chosen was seven. However, many of the cases only have one or two different features chosen, and usually, a larger proportion of the cases have only one top feature chosen across the 10 reps.

```{r}
# Determine the order that the features are chosen within a case and 
# set of input options
sensitivity_chosen <- hamby224_sensitivity_joined %>%
  select(set, situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(set, situation, case, rep, desc(feature_weight_abs)) %>%
  mutate(explainer = rep(c("first", "second", "third"), length(situation) / 3)) %>%
  select(-feature_weight, -feature_weight_abs) %>%
  spread(explainer, feature)
```

```{r}
# Determine and plot the number of features chosen across the 10 reps within 
# a set, input options, and feature level
sensitivity_chosen %>%
  group_by(set, situation, case) %>%
  summarise(first = length(levels(factor(first))),
            second = length(levels(factor(second))),
            third = length(levels(factor(third)))) %>%
  gather(chosen, nfeatures, first:third) %>%
  ggplot(aes(x = situation, fill = factor(nfeatures))) + 
  geom_bar(position = "stack") + 
  facet_grid(set ~ chosen) + 
  labs(x = "Bin Type", y = "Count", fill = "Number of Features") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") + 
  scale_fill_gretchenalbrecht(palette = "winter_light", discrete = TRUE)
```

The plots below need some work, but they contain some interesting information. Right now, I am only concentrating on set 1. We can see that with some lime settings, all cases have the same "best" variable chosen, and other settings have multiple important variables that depend on the case. We can also see that different variables are selected as important depending on the number of bins. It is also interesting to note that when comparing the quantile bins to the equally spaced bins, this plot shows that the equally spaced bins tend to choose the same first variable for all cases. On the other hand, the quantile bins choose different first variables for the cases.

@@

```{r fig.height = 8, fig.width = 10}
hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(2) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")

hamby224_sensitivity_joined %>%
  filter(set == "Set 1") %>%
  droplevels() %>%
  select(situation, case, rep, feature, feature_weight) %>%
  mutate(feature_weight_abs = abs(feature_weight)) %>%
  arrange(situation, case, rep, desc(feature_weight_abs)) %>%
  group_by(situation, case, rep) %>%
  slice(3) %>%
  ungroup() %>%
  group_by(situation, case) %>%
  mutate(nlevels = length(levels(factor(feature)))) %>%
  ungroup() %>%
  arrange(situation, desc(nlevels), case) %>%
  mutate(order = rep(rep(1:length(levels(case)), each = 10), 22)) %>%
  ggplot(aes(x = order, fill = feature)) + 
  geom_bar(position = "stack", width = 1) + 
  coord_flip() + 
  facet_wrap(situation ~ ., ncol = 5) +
  #facet_grid(nlevels ~ situation) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  labs(x = "cases")
```

@@

```{r}
hamby224_test %>% 
  select(rf_features, rfscore, samesource) %>%
  gather(key = feature, value = value, 1:9) %>%
  select(feature, value, rfscore, samesource) %>%
  ggplot(aes(x = value, y = rfscore, color = samesource)) + 
  geom_point() + 
  facet_wrap( ~ feature, scales = "free") +
  labs(x = "Variable Value", y = "Random Forest Score", color = "Same Source?",
       title = "Hamby 224 Testing Data") +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

```{r}
joined_results <- hamby224_lime_results %>%
  select(set, situation, mse, ave_r2) %>%
  full_join(hamby224_sensitivity_results %>%
              group_by(set, situation) %>%
              summarise(mean_sensitivity_mse = mean(mse), 
                        sd_sensitivity_mse = sd(mse)),
            by = c("set", "situation")) %>%
  full_join(hamby224_consistency %>% select(set, situation, mean_nlevels, sd_nlevels), 
            by = c("set", "situation")) %>%
  group_by(set) %>%
  mutate(mse_order = dense_rank(mse),
         ave_r2_order = dense_rank(desc(ave_r2)),
         mean_sensitivity_mse_order = dense_rank(mean_sensitivity_mse),
         mean_nlevels_order = dense_rank(mean_nlevels))
```

```{r}
joined_results %>%
  ungroup() %>%
  filter(set == "Set 1") %>%
  select(situation, mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  arrange(mse_order, mean_sensitivity_mse_order, mean_nlevels_order, ave_r2_order) %>%
  DT::datatable(options = list(pageLength = 12, paging = FALSE, searching = FALSE),
                rownames = FALSE,
                colnames = c("Situation", "MSE", "Mean MSE", "Mean Number of Top Features", 
                             "Mean R2"),
                caption = "Results from Set 1")

@@
